Reproducibility in Plant Pathology

### 2021-09-13 README.rmd
Update README
Update pkgdown site

@@

Adam H Sparks
Senior Research Scientist
Farming Systems Innovation
Primary Industries Development
Department of Primary Industries and Regional Development
Level 6, 1 Nash St., Perth WA 6000

@@

>>>>

### Licensing

@@

Adam H. Sparks
Senior Research Scientist
Farming Systems Innovation
Primary Industries Development
Department of Primary Industries and Regional Development
Level 6.35, 1 Nash St., Perth WA 6000

@@

### Code of Conduct

Please note that the Reproducibility.in.Plant.Pathology project is released with a [Contributor Code of Conduct](https://openplantpathology.github.io/Reproducible.Plant.Pathology/CODE_OF_CONDUCT.html).
By contributing to this project, you agree to abide by its terms.
